Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-04 ch04-lrmhinf/lrmhinf.tex
Add figures about vibration isolation

Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability.
An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
The underlying feedback control principle is skyhook damping~\citep{Karnopp1995}. 
However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.

@@

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
The \gls{AVIS} consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
Six geophones measure the payload velocity and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform.
Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
%TODO: include benchmark section about vibration isolation

>>>>

Robustness is of key importance in feedback controlled systems, since feedback can lead to performance degradation or even closed-loop instability.
An important example includes an \gls{AVIS}, where feedback is used to isolate high-precision equipment from external disturbances. 
The underlying feedback control principle is skyhook damping~\citep{Karnopp1995,Collette2011}. 
However, the performance of skyhook damping is limited by high-frequent lightly-damped parasitic resonance phenomena.
Such model uncertainties can be taken into account explicitly in a robust control design~\citep{Zhang2005HybridAvis} for approaches based on \Hinf{} optimization.
However, the uncertainty estimation in these references is based on rough prior assumptions and may be inaccurate. 
On the one hand, this can lead to potentially dangerous results, since no stability and performance guarantees can be given if the estimated uncertainty is too small. 
On the other hand, this can also lead to overly conservative controllers if the estimated uncertainty is too large.

@@

\section{Application to an \glsentryname{AVIS}}
\label{sec:lrmhinf:measurement}
The proposed method is illustrated on the \gls{AVIS} shown in \figref{fig:lrmhinf:avis}.
%TODO: include benchmark section about vibration isolation
The broad aim of vibration isolation~\citep{Karnopp1995,Collette2011} is to suppress vibrations such that a certain payload (e.g. passengers in a car, sensitive equipment such as atomic force microscopes or wafer-scanners used for lithography) is not disturbed by vibrations generated by either the payload itself or by the outside world.

\begin{figure}
 \centering
  \setlength{\figurewidth}{0.45\columnwidth}
  \begin{subfigure}[b]{0.49\columnwidth}
  \remakeNextFigure
    \input{\thisDir/figs/vibrationisolation-classical.tikz}
    \caption{Using relative velocity measurements.}  
  \end{subfigure}
  \begin{subfigure}[b]{0.49\columnwidth}
  \remakeNextFigure
    \input{\thisDir/figs/vibrationisolation-skyhook.tikz}
    \caption{Using an absolute velocity measurements.}  
  \end{subfigure}
  \caption{Vibration isolation}
\end{figure}
%TODO: include benchmark section about vibration isolation

The particular \gls{AVIS} used for the experiments, consists of a support fixed to the ground and a payload platform, suspended on airmounts (see \figref{fig:lrmhinf:avis:details}), that is free to move in six degrees of freedom.
Six geophones measure the payload velocity in an absolute reference frame and eight linear motors (see \figref{fig:lrmhinf:avis:details}) allow to actively compensate for vibration of the platform using the principle of `sky-hook damping'.
Please refer to \appref{app:avis-setup} for more details regarding the mechanical set-up.
To facilitate the presentation, only the vertical translation, i.e. a \gls{SISO} system,  is considered.
